### 2018-06-08 5_eval.tex
fix infinite recursion on footnotes.
Fix titles spacing and some pics floating.

As another example of program liable for analysis consider the Dekker's algorithm for mutual exclusion of two processes, originally described by Dijkstra~\cite{dijkstra1962over}; the program is presented in Appendix~\ref{apx:dekker}.
For testing \porthos[1], we used the same file in old \porthos{} input language (\texttt{dekker.pts}), which was used in evaluation tests in the original paper~\cite{Porthos17a}.
For performing tests, \porthos[2] was slightly modified in the branch \textit{ay/test-timing}%
\footnote{The modifications were pushed into the \porthos[1] repository \url{github.com/hernanponcedeleon/Dat3M}} %
%
for printing detailed timing information and statistics about number of events (commit f8a6c97f) and writing this information in strict \textit{json} format so that it can be easily processed later by a script that analyses and prints the results (commit 48ba7161).
The version of \porthos[2] used for the tests is actual up to commit 01dde6b1 of the \porthos[2] GitHub repository.
Both \porthos[1] and \porthos[2] are run in the state reachability mode for TSO memory model (see sample output of \porthos[2] in Appendix~\ref{apx:output}).

@@

\begin{figure}%[t]
\centering
\begin{minipage}[t]{.49\textwidth}%for preventing overfull
\begin{lstlisting}
{ int x = 0; int y = 0;}

P0(volatile int* y, volatile int* x) {
  int r0;
  WRITE_ONCE(*x,1);
  r0 = READ_ONCE(*y);
}

P1(volatile int* y, volatile int* x) {
  int r0;
  WRITE_ONCE(*y,1);
  r0 = READ_ONCE(*x);
}

@@

>>>>

As another example of program liable for analysis consider the Dekker's algorithm for mutual exclusion of two processes, originally described by Dijkstra~\cite{dijkstra1962over}; the program is presented in Appendix~\ref{apx:dekker}.
For testing \porthos[1], we used the same file in old \porthos{} input language (\texttt{dekker.pts}), which was used in evaluation tests in the original paper~\cite{Porthos17a}.
For performing tests, \porthos[2] was slightly modified in the branch \textit{ay/test-timing}%
\myfootnote{The modifications were pushed into the \porthos[1] repository \url{github.com/hernanponcedeleon/Dat3M}} %
%
for printing detailed timing information and statistics about number of events (commit f8a6c97f) and writing this information in strict \textit{json} format so that it can be easily processed later by a script that analyses and prints the results (commit 48ba7161).
The version of \porthos[2] used for the tests is actual up to commit 01dde6b1 of the \porthos[2] GitHub repository.
Both \porthos[1] and \porthos[2] are run in the state reachability mode for TSO memory model (see sample output of \porthos[2] in Appendix~\ref{apx:output}).

@@

@@

\begin{figure}[h]
\centering
\begin{minipage}[t]{.49\textwidth}%for preventing overfull
\begin{lstlisting}
{ int x = 0; int y = 0;}

P0(volatile int& y, volatile int& x) {
  int r0;
  WRITE_ONCE(x,1);
  r0 = READ_ONCE(y);
}

P1(volatile int& y, volatile int& x) {
  int r0;
  WRITE_ONCE(y,1);
  r0 = READ_ONCE(x);
}
